Faithful Variable Screening for High-Dimensional Convex Regression

### 2014-06-29 tex/scam/introduction.tex
minor updates
test

We consider the problem of estimating a convex function of several
variables from noisy values of the function at a finite sample of
input points.  Recent work \cite{Guntu:12,Guntu:13} shows that the
minimax rate for convex function estimation in $p$ dimensions is
$n^{-4/(4+p)}$.  Loosely speaking, this shows that the
geometric convexity constraint is statistically equivalent to
requiring two derivatives of the function, and thus is
subject to the same curse of dimensionality.
However, if the function is sparse, with $s\ll p$ relevant variables,
then the faster rate $n^{-4/(4+s)}$ may be achievable if the $s$
variables can be identified.  To determine the relevant variables, we
show that it suffices to estimate a sum of $p$ one-dimensional convex
functions, leading to significant computational and statistical
advantages.  In addition, we introduce algorithms and supporting
statistical theory for a practical, effective approach to this
variable selection problem.

>>>>

Shape restrictions such as monotonicity, convexity, and concavity
provide a natural way of limiting the complexity of many statistical
estimation problem.  Shape-constrained estimation is not as well
understood as more traditional nonparametric estimation involving
smoothness constraints.  For instance, as of this writing the minimax
rate of convergence for multivariate convex regression has yet to be
rigorously established in full generality.  Even the one-dimensional
case is challenging, and has been of recent interest
\citep{guntusen:13}.

In this paper we study the problem of variable selection
in convex regression.   Assuming that the regression
function is convex and sparse, in order to select the
relevant variables we 
show that it suffices to estimate a sum of $p$ one-dimensional convex
functions, leading to significant computational and statistical
advantages .  In addition, we introduce algorithms and supporting
statistical theory for a practical, effective approach to this
variable selection problem.
